Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Reformatted the GLAD/EDGI, NBR and RAMP ethnicity retro graph

GLAD.prepan %>% 
  ggplot(aes(x = Ethnicity_collapsed)) +
  geom_bar(fill = COPINGpalette6) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Ethnic distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   labels = ethnicity_levels)

@@

dat.retro %>% 
  ggplot(aes(x = Ethnicity_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Ethnic distribution of the retro cohorts",
       x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   labels = ethnicity_levels) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

>>>>

GLAD.prepan %>% 
  ggplot(aes(x = Ethnicity_collapsed)) +
  geom_bar(fill = COPINGpalette6) +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Ethnic distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   labels = ethnicity_levels)

@@

dat.retro_ethnicity_plot <- dat.retro %>% 
  group_by(Sample_plot, Ethnicity_collapsed) %>% 
  summarise(n = n()) %>% 
  drop_na()

dat.retro_ethnicity_plot %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   labels = ethnicity_levels) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n), 
            position = position_dodge(width=0.9), 
            vjust=-0.25)
